---
title: "PML_Week3"
author: "Sejin Park"
date: "2015. 9. 27."
output: html_document
---
## measures of impurify

분류를 위한 나무모형 - 각노드에 속하는 자료가 분할하면서 자라나게 된다. 
분할 후 생성된 노드에 속하는 자료의 순수도(purity)가 가장 크게 증가하도록 재귀적으로 recursively 진행되는데, 이는 분할 기준이 되는 변수와 분할의 위치를 결정해야 하는 반복적 작업으로 표현될 수 있다. 
여기서 순수도의 증가란 분할 후 각 노드에 속하는 자료의 구성이 이산형의 목표변수(target variable)를 기준으로 어느 한 클래스(class)에만 속하는 자료의 비율이 높다는 의미이기도 하지만, 대부분의 나무모형 알고리즘에서는 순수도를 자료의 혼란도나 복잡도의 반대 개념으로 정의된 불순도 측도를 사용하고 있다. 
즉, 나무모형에서 순수도의 최대증가란 분할 후 불순도(impurity)의 감소폭이 가장 크다는 의미이다. 

## 불순도 함수 

나무모형 T의 전체 불순도 D(T)는 다음과 같이 표현된다. 

여기서 G는 나무모형 T의 최종노드의 집합이고 p(g)는 최종노드 g에 속할 확률이다. 예를 들어, 전체 자료 100개 중 최종 노드 g에 20개의 자료가 포함된다면 p(g)=20/100 = 0.2 이다. 그리고 g는 불순도 함수이다. 


## QUIZ 3
## Q1
Load the cell segmentation data from the AppliedPredictiveModeling package using the 

1. Subset the data to a training set and testing set based on the Case variable in the data set. 
2. Set the seed to 125 and fit a CART model with the rpart method using all predictor variables and default caret settings. 
3. In the final model what would be the final model prediction for cases with the following variable values:
a. TotalIntench2 = 23,000; FiberWidthCh1 = 10; PerimStatusCh1=2 
b. TotalIntench2 = 50,000; FiberWidthCh1 = 10;VarIntenCh4 = 100 
c. TotalIntench2 = 57,000; FiberWidthCh1 = 8;VarIntenCh4 = 100 
d. FiberWidthCh1 = 8;VarIntenCh4 = 100; PerimStatusCh1=2 
```{r}
library(AppliedPredictiveModeling)
data("segmentationOriginal")
library(caret)
str(segmentationOriginal); names(segmentationOriginal)
set.seed(125)
#inTrain <- createDataPartition(y=segmentationOriginal$Case, p=0.7, list=FALSE)
inTrain <- segmentationOriginal$Case == "Train"
training <- segmentationOriginal[inTrain,][,-c(2)]
testing <- segmentationOriginal[-inTrain,][,-c(2)]
modFit <- train(Class ~ ., method="rpart", data=training)
print(modFit$finalModel)
#rattle::fancyRpartPlot(modFit$finalModel)
```
a. PS 
b. WS 
c. PS
d. Not possible to predict
## Q2
If K is small in a K-fold cross validation is the bias in the estimate of out-of-sample (test set) accuracy smaller or bigger? If K is small is the variance in the estimate of out-of-sample (test set) accuracy smaller or bigger. Is K large or small in leave one out cross validation?

The bias is larger and the variance is smaller. Under leave one out cross validation K is equal to one.

## Q3
```{r}
library(pgmm)
data(olive)
olive = olive[,-1]
newdata = as.data.frame(t(colMeans(olive)))
modFit <- train(Area ~ ., method="rpart",data=olive)
print(modFit$finalModel)
```
2.783. It is strange because Area should be a qualitative variable - but tree is reporting the average value of Area as a numeric variable in the leaf predicted for newdata

## Q4
Load the South Africa Heart Disease Data and create training and test sets with the following code:
```{r}
library(ElemStatLearn)
data(SAheart)
str(SAheart)
set.seed(8484)
train = sample(1:dim(SAheart)[1],size=dim(SAheart)[1]/2,replace=F)
trainSA = SAheart[train,]
testSA = SAheart[-train,]
set.seed(13234)
trclass <- c("chd","age","alcohol","obesity","tobacco","typea","ldl")
modelFit <- glm(chd ~ ., data=trainSA[,trclass],family=binomial()) 
predict(modelFit, type="response")

```
Then set the seed to 13234 and fit a logistic regression model (method="glm", be sure to specify family="binomial") with Coronary Heart Disease (chd) as the outcome and age at onset, current alcohol consumption, obesity levels, cumulative tabacco, type-A behavior, and low density lipoprotein cholesterol as predictors. Calculate the misclassification rate for your model using this function and a prediction on the "response" scale:

```{r}
missClass = function(values,prediction){sum(((prediction > 0.5)*1) != values)/length(values)}
predict(modelFit, type="response")
```
What is the misclassification rate on the training set? What is the misclassification rate on the test set?